Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
slight wording change
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51105 72bbbca6-d526-0410-a7d9-f06f51895060

The three languages for which transducers were developed belong to the Northwestern branch of the Turkic family, which is often referred to as the Kypchak branch.  This branch can be divided into three sub-branches.  Kumyk is a member of the Western Kypchak group, Tatar is a member of the Northern Kypchak group, and Kazakh is a member of the Southern Kypchak group \citep[82-83]{histofturkic}.\footnote{It is the professional opinion of the authors of this paper that Kyrgyz constitutes a fourth branch.}   The geographic distribution of the languages is shown in map~\ref{map1}.
%As such, each of these three languages represents one of the three branches of Kypchak.

>>>>

The three languages for which transducers were developed belong to the Northwestern branch of the Turkic family, which is often referred to as the Kypchak branch.  This branch can be divided into three sub-branches.  Kumyk is a member of the Western Kypchak group, Tatar is a member of the Northern Kypchak group, and Kazakh is a member of the Southern Kypchak group \citep[82-83]{histofturkic}.\footnote{It is the professional opinion of the authors of this paper that Kyrgyz constitutes a fourth branch of Kypchak.}   The geographic distribution of the languages is shown in map~\ref{map1}.
%As such, each of these three languages represents one of the three branches of Kypchak.
